A comprehensive Schizosaccharomyces pombe atlas of physical transcription factor interactions with proteins and DNA

### 2025-03-21 index.qmd
update links to publication and data
Co-authored-by: Charlotte Soneson <charlottesoneson@gmail.com>
Co-authored-by: Michael Stadler <stadler.michael@gmail.com>

## Links to raw data

@@

@@

The accompanying manuscript is available at:

- bioRxiv
- ...

>>>>

## Links to raw data and strain library

@@

The *S. pombe* strain library is available as set **FYS8** from [NBRP – Yeast, Japan](https://yeast.nig.ac.jp/yeast/fy/StrainSetAllItemsList.jsf)

@@

The accompanying manuscript is:
**A comprehensive Schizosaccharomyces pombe atlas of physical transcription factor
interactions with proteins and chromatin** Skribbe, Soneson, Stadler et al.
*Molecular Cell* (2025)

and is available from:

- [DOI: 10.1016/j.molcel.2025.01.032](https://doi.org/10.1016/j.molcel.2025.01.032)
- [PubMed 40015273](https://pubmed.ncbi.nlm.nih.gov/40015273/)
- [HTML (fulltext)](https://www.cell.com/molecular-cell/fulltext/S1097-2765(25)00099-1)
- [bioRxiv 2024.08.20.607873](https://doi.org/10.1101/2024.08.20.607873)
